### 2020-04-08 Report/aws_325ghz_study.tex
A bit of new report text.

\subsubsection{Fascod}
%
The Fascod dataset \citep{anderson1986afgl} was used to represent different
climate zones in overview calculations. The dataset consists of profiles of
pressure, temperature and volume mixing ratio profiles of various atmospheric
gases. Five climatoligies were used: tropical (TRO), mid-latitude summer (MLS),
mid-latitude winter (MLW), sub-arctic summer (SAS), and sub-arctic winter
(SAW). No hydrometeors were included in simulations involving Fascod.

@@

This approach for generating atmospheric scenarios has been used by us since
\citet{rydberg:nonga:09}, and more recently in e.g.\
citet{eriksson:towar:20,barlakas:three:20}. It is also used in
\citet{ekelund:using:20}, where the approach is described more in detail. In
the cited articles, the sensor's footprint has been considered in varying
degree, as ``beam filling'' must be considered at high impact of hydrometeors.
As clear-sky and weak cloud interference are in focus in this study, and to
save calculation time, instead CloudSat data were averaged over 10\,km to form
the atmospheric cases and standard 1D radiative transfer calculations are
applied on each case (instead of applying an independent beam approximation
inside a 2D or 3D atmosphere as done in cited works).

@@

\subsection{Overview of the frequency bands}
%
The simulations involving Fascod were done using a fixed satellite observation
angle of 155$^\circ$ (from zenith) \dots

\begin{figure}[p]
  \centering
  \includegraphics[width=0.7\textwidth]{fascod_tb_r000}
  \caption{dd}
  \label{fig:tb:r00}
\end{figure}
\begin{figure}[p]
  \centering
  \includegraphics[width=0.7\textwidth]{fascod_tb_r050}
  \caption{Same as figure above, but with a surface reflectivity of 0.5.}
  \label{fig:tb:r00}
\end{figure}

>>>>

\subsubsection{Fascod}
\label{sec:fascod}
%
The Fascod dataset \citep{anderson1986afgl} was used to represent different
climate zones in overview calculations. The dataset consists of profiles of
pressure, temperature and volume mixing ratio profiles of various atmospheric
gases. Five climatoligies were used: tropical (TRO), mid-latitude summer (MLS),
mid-latitude winter (MLW), sub-arctic summer (SAS), and sub-arctic winter
(SAW). No hydrometeors were included in simulations involving Fascod.

@@

This approach for generating atmospheric scenarios has been used by us since
\citet{rydberg:nonga:09}, and more recently in e.g.\
\citet{eriksson:towar:20,barlakas:three:20}. It is also used in
\citet{ekelund:using:20}, where the approach is described more in detail. In
the cited articles, the sensor's footprint has been considered in varying
degree, as ``beam filling'' must be considered at high impact of hydrometeors.
As clear-sky and weak cloud interference are in focus in this study, and to
save calculation time, instead CloudSat data were averaged over 10\,km to form
the atmospheric cases and standard 1D radiative transfer calculations are
applied on each case (instead of applying an independent beam approximation
inside a 2D or 3D atmosphere as done in cited works).

@@

\subsection{Overview of the 183, 229 and 325\,GHz bands}
%
The simulations in this sction are based on five Fascod climate scenarios
(Sec.~\ref{sec:fascod}), and performed with a fixed sensor viewing angle of
25$^\circ$. No hydrometeors are included. For simpler interpretetation of the
results, the reflectivity is set to have no frequency variation, i.e.\ the same
value is applied for all bands. The reflective is varied between 0 and 0.5.

\subsubsection{Clear-sky brightness temperatures}
%
Figure~\ref{fig:tb:r00} shows brightness temperatures over the three bands, for
a reflectivity of 0 (i.e.\ a blackbody surface). The figure takes into account
that the 183\,GHz channels of AWS are of single-sideband character, while for
229 and 325\,GHz averages of upper and lower sidebands are shown, plotted as
a function from the centre frequency on the lower side.

\begin{figure}[p]
  \centering
  \includegraphics[width=0.75\textwidth]{fascod_tb_r000}
  \caption{Solid lines show brightness temperatures for the lower wing of the
    183.31\,GHz transition. Dashed lines represent double-sideband measurements
    around 325.15\,GHz, with the mean of upper and lower band shown on the low
    side. Dash-dotted lines represent double-sideband measurements around
    229.00\,GHz in the same manner, but only over the bandwidth of the
    potential channel. For all three bands, spectra for all five
    Fascod scenarios are included.}
  \label{fig:tb:r00}
\end{figure}
\begin{figure}[p]
  \centering
  \includegraphics[width=0.75\textwidth]{fascod_tb_r050}
  \caption{Same as figure above, but with a surface reflectivity of 0.5.}
  \label{fig:tb:r00}
\end{figure}

For 183 and 325\,GHz the brightness temperatures increase when moving away from
the centre frequency of the transition. The ``kinks'' in the spectra correspond
to ozone transitions, that are both more frequent and stronger in the 325\,GHz
range than in the 183\,GHz one. See Fig.~1 of \citet{eriksson:towar:20} for how
the ozone transitions are distribbuted between the lower and uper 325\,GHz sideband. 
The spectra of 183 and 325\,GHz deviate little close to the trasition
frequency, showing that the two frequencies are of similar strength, though the
325\,GHz one is slightly weaker. The higher deviation further out in the wings
is due to different contribution of far wing and continuum absorption. This
contribution is higher at 325\,GHz. The 229\,GHz brightness temperatures is
higher than any value around 183 and 325\,GHz, as expected 229\,GHz being a
window channel.

In Figure~\ref{fig:tb:r00} the surface reflectivity is changed to 0.5, which
should roughly correspond to the highest reflectivity encountered at these
frequencies. The differences between the two figures are small for 183 and
325\,GHz tor the tropical and the two summer scenarios. On the other hand,
there is a clear impact in the wing part of 183\,GHz for the two winter
scenarios. The same is true for 340\,GHz, but the influence of the surface
reflectivity is considerably lower. [* Comment somewhere on the implications of
this for retrievals at high latitudes *] Beside for the tropical case, for
229\,GHz there is a pronounced dependendency of the surface reflectivity, e.g.\
about 35\,K for mid-latitude winter.

\subsubsection{Clear-sky relative humidity weighting functions}
%
\dots

\subsubsection{Clear-sky transmissivities to space}
%
\dots
